---
title: "FLARE GEB Study Area"
author: "Anna Talucci"
date: "8/30/2021"
output: html_document
---

# Overview

Skeleton for developing a map figure 

This script is reliant on
* `Rproj` and therefore the `wd()`does not have to be set
* Relative path names "../folder-name/file-name.ext"
* This script is reliant on the following folders 
    +"../scripts/" --this houses all scripts written in RMarkdown
    +"../data/shapfiles/" --this houses shape files
    +"../figures/
* Please reference the Git Hub repository called **FLARE-UAV-veg** to see the file structure used here

# Packages
```{r}
library(rgdal)
library(raster)
library(ggplot2)
library(maptools)
library(rgeos)
library(sp)
library(mapproj)
library(sf)
library(RStoolbox)
library(ggspatial)
library(cowplot)
library(dplyr)
library(RColorBrewer)
```


# Projections 

Russia Equal area projection

```{r}
ea_ru = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs "
```


# Data

## World map
https://datacatalog.worldbank.org/dataset/world-bank-official-boundaries

```{r}
asia = st_read("../data/Asia_ea/asia_ea.shp", "asia_ea")
```

## Ecozones
```{r}
eco = st_read("../data/EcozonesNE/NstCkmtEcozones.shp", "NstCkmtEcozones")
```

```{r}
head(eco)
```

## Cities
```{r}
chersky = st_sf(geometry = st_sfc(st_point(c(161.399713, 68.739907))), crs = ("+proj=longlat +datum=WGS84 +no_defs"))

chersky
```

```{r}
yakutsk = st_sf(geometry = st_sfc(st_point(c(129.7422, 62.0397))), crs = ("+proj=longlat +datum=WGS84 +no_defs"))

yakutsk
```



## Arctic Circle 
Arctic Circle shapefile came from [Natural Earth](https://www.naturalearthdata.com/downloads/110m-physical-vectors/110m-geographic-lines/)

```{r}
circle = st_read("../data/ne_110m_geographic_lines/ne_110m_geographic_lines.shp", "ne_110m_geographic_lines") 
```
```{r}
arctic = circle %>% filter(name=="Arctic Circle")
```

## Permafrost
```{r}
permafrost = st_read("../data/permafrost/permaice.shp", "permaice") 
```

## Yedoma
```{r}
yedoma1 = st_read("../data/IRYP_v1_shapefiles/QG1000k_yedoma_russia.shp", "QG1000k_yedoma_russia") 
yedoma2 = st_read("../data/IRYP_v1_shapefiles/QG2500k_yedoma_russia.shp", "QG2500k_yedoma_russia") 
yedoma3 = st_read("../data/IRYP_v1_shapefiles/SG500k_yedoma_russia.shp", "SG500k_yedoma_russia") 
```

```{r}
head(yedoma1)
head(yedoma2)
head(yedoma3)

```


```{r}
yedoma = dplyr::bind_rows(yedoma1, yedoma2, yedoma3)

```

## Fires

```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2020.shp", "NESiberiaFires2020")
```

# Raster
```{r}
vegWgs<-raster("../data/VegetationRasters/FLARE-Eco-Forest-Percent-clip-2000-WGS.tif")
```

# Raster Projection


```{r}
vegwgs_reprj <- projectRaster(vegWgs, crs = crs(ea_ru))
```

# Filter Data

## Filter countries
```{r}
target_cnty = c("Mongolia", "Kazakhstan", "Japan", "People's Republic of China", "Russia", "Uzbekistan")
```

```{r}
target_iso = c("MN", "RU", "CN", "KZ", "KG", "UZ", "JP", "TM")
```

```{r}
target = c("Asia", "Europe")
```

Filter for all
```{r eval=FALSE, include=FALSE}
asia  = wrld %>% 
  filter(CONTINENT %in% target) %>%
  dplyr::select( OBJECTID:FORMAL_EN, NAME_EN, ISO_A2, CONTINENT:REGION_WB, Shape_Leng:geometry) 
```

```{r eval=FALSE, include=FALSE}
asia
```

## Filter ecozones
```{r eval=FALSE, include=FALSE}
eco
```

```{r}
ckmt = eco %>% filter(eco_code == "CKMT")
nst = eco %>% filter(eco_code=="NST")
eco = eco %>% filter(eco_code=="NST" | eco_code=="CKMT")
```


## Filter Permafrost
```{r}
perma_con = permafrost %>% 
  filter(EXTENT =="C") 
```

```{r}
perma_dis = permafrost %>% 
  filter(EXTENT=="D") 
```

# Reproject Shapefiles

```{r}
asia_ea = st_transform(asia, crs = ea_ru)
ch_ea = st_transform(chersky, crs = ea_ru)
yak_ea = st_transform(yakutsk, crs = ea_ru)
ckmt_ea = st_transform(ckmt, crs = ea_ru)
nst_ea = st_transform(nst, crs = ea_ru)
eco_ea = st_transform(eco, crs = ea_ru)
artic_ea = st_transform(arctic, crs = ea_ru)
yedoma_ea = st_transform(yedoma, crs = ea_ru) 
perma_con_ea = st_transform(perma_con, crs = ea_ru) 
perma_dis_ea = st_transform(perma_dis, crs = ea_ru) 
fires_ea = st_transform(fires, crs = ea_ru) 

```
## Write Eco_ea to file

```{r eval=FALSE, include=FALSE}
st_write(eco_ea, "../outputs/NST_CKMT_Eco/NST_CKMT_Eco.shp", driver="ESRI Shapefile") 
```

```{r}
plot(asia_ea$geometry)
```


# Color Palettes
```{r}
# Assign color to a object for repeat use/ ease of changing
myCol = c('#b2e2e2','#66c2a4','#2ca25f','#006d2c')
myCol2 = c('darkolivegreen1','lightgreen','springgreen4','darkgreen')
```
```{r}
ecoPalette <- c("#b5b35c", "#556b2f")
```
```{r}
cbEcoPal = c("#E1BE6A", "#40B0A6")
```

# Maps
## Ecozones NST and CKMT

```{r fig.height=2.5, fig.width=2}
map1 = ggplot() +
    geom_sf(data = asia_ea, fill = "#C0C0C0", colour="#A9AB9D") +
    geom_sf(data = eco_ea,  aes(fill=ECO_NAME), colour = NA) +
  scale_fill_manual(values=cbEcoPal, labels = c("CKMT", "NST")) +
    geom_sf(data=artic_ea, fill=NA, colour = "#FFFFFF", lwd=1, linetype="dashed") +
    
  geom_sf(data=ch_ea, colour="#000000") +
  geom_sf(data=yak_ea, colour="#000000") +
  coord_sf(xlim = c(-1334205, 3333752), ylim = c(-522562, 3293703)) +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), 
        panel.background = element_rect(fill = "#C5D8D7")) +
  theme(legend.title = element_blank(), 
        legend.text=element_text(size=5),
        legend.position = c(.7, .08), 
        legend.key.height = unit(.05, 'in'), 
        legend.key.width = unit(.05, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0)),
         axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y=element_blank(), 
        axis.ticks.y=element_blank()) +
  guides(fill=guide_legend(ncol=2,byrow=FALSE))

map1
```

## map 2 permafrost and fire
xmin: 1024425 ymin: 1044414 xmax: 2696481 ymax: 2611519
```{r fig.height=5, fig.width=6}
map2 <- ggplot() +
    geom_sf(data = asia_ea, fill = "#C0C0C0", colour="#A9AB9D") +
  geom_sf(data = perma_con_ea, fill = "#98eff9", colour= NA) +
  geom_sf(data = perma_dis_ea, fill = "#dcf3ff", colour= NA) +
  geom_sf(data = yedoma_ea, fill = "#0EC0A6", colour= NA) +
  geom_sf(data = fires_ea,  fill=NA, colour = "#c62b27", lwd=0.2) +

    geom_sf(data=artic_ea, fill=NA, colour = "#FFFFFF", lwd=1, linetype="dashed") +
 
  coord_sf(xlim = c(1024425, 2696481), ylim = c(1044414, 2611519)) +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", size = 0.5), panel.background = element_rect(fill = "#C5D8D7")) +
  annotation_scale(location = "bl", line_width = .25, height = unit(0.15, "cm"), text_cex = 0.5, text_face = "plain", text_family = "sans", text_col = "black") +
  
  theme(legend.title = element_blank(), 
        legend.position = c(.1, .25), 
        legend.box="vertical",
        legend.background = element_rect(fill=alpha('white', 0.0)),
         axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y=element_blank(), 
        axis.ticks.y=element_blank()) 
  


map2
```

## Map 3
```{r fig.height=5, fig.width=6}
map3 <- ggplot() +
    geom_sf(data = asia_ea, fill = "#C0C0C0", colour="#A9AB9D") +
  geom_sf(data = perma_con_ea, fill = "#98eff9", colour= NA) +
  geom_sf(data = perma_dis_ea, fill = "#dcf3ff", colour= NA) +
  geom_sf(data = yedoma_ea, fill = "#0EC0A6", colour= NA) +
  geom_sf(data = fires_ea,  fill=NA, colour = "#c62b27") +

    geom_sf(data=artic_ea, fill=NA, colour = "#FFFFFF", lwd=1, linetype="dashed") +
  geom_sf(data=ch_ea, colour="#000000") +
  coord_sf(xlim = c(924425, 2796481), ylim = c(744414, 2711519)) +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", size = 0.5), panel.background = element_rect(fill = "#C5D8D7")) +
  annotation_scale(location = "bl", width_hint = 0.2, text_size = 6, text_face = "bold", text_family = "sans", text_col = "black") +
  
  theme(legend.title = element_blank(), 
        legend.position = c(.1, .25), 
        legend.box="vertical",
        legend.background = element_rect(fill=alpha('white', 0.0)),
         axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y=element_blank(), 
        axis.ticks.y=element_blank()) 
  


map3
```
## Vegetation Map

```{r fig.height=3.5, fig.width=3}
p1 = ggplot()+
  geom_sf(data=asia, fill = "#C0C0C0", colour="#A9AB9D") +
  layer_spatial(vegwgs_reprj) +
  scale_fill_gradientn(colours=myCol2,  limits=c(1,100), breaks=c(25, 50,  75, 100), na.value = "transparent", name="Percent\ntree cover") +
  geom_sf(data=fires, fill=NA, colour = "#c62b27", lwd=0.2) +
  coord_sf(xlim = c(1024425, 2696481), ylim = c(1044414, 2611519)) +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", size = 0.5), panel.background = element_rect(fill = "#C5D8D7")) +
  
  theme(legend.title = element_text( size=8), 
        legend.text=element_text(size=6),
        legend.position = c(.16, .8), 
        legend.box="vertical",
        legend.background = element_rect(fill=alpha('white', 0.5)),
        legend.key.height = unit(.07, 'in'), 
        legend.key.width = unit(.07, 'in'),
         axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y=element_blank(), 
        axis.ticks.y=element_blank()) 
   
p1
```
```{r}
ggsave("../figures/FLARE-GEB-VegFireMap.png", plot = p1, width = 3, height = 3.5, units = c("in"), dpi = 600)
```

## Legend
```{r fig.height=4.5, fig.width=6}
legend1 =  ggplot() +
    geom_sf(data = asia_ea, fill = "#C0C0C0", colour="#A9AB9D") +
  geom_sf(data = perma_con_ea, aes(fill = "Continuous"), colour= NA) +
  geom_sf(data = perma_dis_ea, aes(fill = "Discontinuous"), colour= NA) +
  geom_sf(data = yedoma_ea, aes(fill = "Yedoma"), colour= NA) +
  geom_sf(data = fires_ea,  aes(fill="Fires"), colour = NA) +
  
  scale_fill_manual(values=c("Continuous" = "#98eff9", "Discontinuous" = "#dcf3ff", "Yedoma" = "#0EC0A6", "Fires" = "#c62b27"),   breaks = c("Continuous", "Discontinuous", "Yedoma", "Fires"),labels = c("Continuous", "Discontinuous", "Yedoma", "Fires"),name = "Permafrost      2020 Fires") +     
  
   
    geom_sf(data=artic_ea, fill=NA, colour = "#FFFFFF", lwd=1, linetype="dashed") +
    
  coord_sf(xlim = c(924425, 2596481), ylim = c(1044414, 2611519)) +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), 
        panel.background = element_rect(fill = "#C5D8D7")) +
  annotation_scale(location = "bl", width_hint = 0.25, text_size = 12, text_face = "bold", text_family = "sans", text_col = "white") +
  theme(legend.title = element_text( size=6), 
        legend.text=element_text(size=4), 
        legend.position = c(.33, .9), 
        legend.key.height = unit(.07, 'in'), 
        legend.key.width = unit(.07, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.9)),
         axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y=element_blank(), 
        axis.ticks.y=element_blank()) +
  guides(fill=guide_legend(nrow=3, byrow=FALSE))

legend1
```

# Combine Map and Legend

## Ecozones
```{r fig.height=2.5, fig.width=2}
fig_eco = cowplot::ggdraw(map1) + 
  draw_label(label="Cherskiy", fontfamily = "sans", fontface = "plain", color = "black", size = 6,  x=.63, y=.69) +
  draw_label(label="Yakutsk", fontfamily = "sans", fontface = "plain", color = "black", size = 6,  x=.5, y=.46) +
  draw_label(label=(expression(paste(70*degree,"N"))), fontfamily = "sans", fontface = "plain", color = "black",angle= 70, size = 5,  x=.72, y=.77) +
  draw_label(label=(expression(paste(60*degree,"N"))), fontfamily = "sans", fontface = "plain", color = "black",angle= 60, size = 5,  x=.91, y=.69) +
  draw_label(label=(expression(paste(50*degree,"N"))), fontfamily = "sans", fontface = "plain", color = "black",angle= 45, size = 5,  x=.89, y=.41) +
  draw_label(label="Arctic Circle", fontfamily = "sans", fontface = "plain", color = "white", size = 6,  x=.33, y=.52) +
  draw_label(label="Russia", fontfamily = "sans", fontface = "plain", color = "black", size = 7, x=.36, y=.4) 

fig_eco
```

```{r}
ggsave("../figures/FLARE-GEB-EcozoneMap.png", plot = fig_eco, width = 2, height = 2.5, units = c("in"), dpi = 600)
```

## Permafrost and fire
```{r}
legend1 <- get_legend(legend1)
```

```{r fig.height=3.5, fig.width=3}
fig_fires = cowplot::ggdraw(map2) + 
  draw_plot(legend1, x=.15, y=.68, width=.3, height=.1) 

fig_fires
```

```{r}
ggsave("../figures/FLARE-GEB-PermafrostFireMap.png", plot = fig_fires, width = 3, height = 3.5, units = c("in"), dpi = 600)
```




## Figure Maps only
ggdraw(xlim = c(0, 6), ylim = c(0, 5)) +

```{r fig.height=7, fig.width=6}
fig2 = ggdraw(xlim = c(0, 6), ylim = c(0, 7)) +
  draw_plot(fig_eco, x = .1, y = 3.51, width = 3, height = 3.5) +
  draw_plot(p1, x= 3.1, y= 3.51, width=3, height = 3.5) +
  draw_plot(fig_fires, x = 0.5, y = -0.02, width = 5, height = 3.5, scale = 1.05) +


  draw_label("(a)", x = 0.25, y = 6.8, fontfamily = "sans", fontface = "bold", color = "black", size = 14) +
  draw_label("(b)", x = 3.25, y = 6.8, fontfamily = "sans", fontface = "bold", color = "black", size = 14) +
  draw_label("(c)", x = 0.25, y = 4.2, fontfamily = "sans", fontface = "bold", color = "black", size = 14)

fig2
```



```{r}
ggsave("../figures/FLARE-GEB-StudyAreaMap.png", plot = fig2, width = 6, height = 7, units = c("in"), dpi = 600)
```