---
title: "MODIS-BurnedArea"
author: "Anna Talucci"
date: "5/20/2021"
output: html_document
---

# Overview

Skeleton for developing a map figure for FLARE UAS vegetation paper

This script is reliant on
* `Rproj` and therefore the `wd()`does not have to be set
* Relative path names "../folder-name/file-name.ext"
* This script is reliant on the following folders 
    +"../scripts/" --this houses all scripts written in RMarkdown
    +"../data/shapfiles/" --this houses shape files
    +"../figures/
* Please reference the Git Hub repository called **FLARE-UAV-veg** to see the file structure used here

# Packages
```{r}
library(rgdal)
library(raster)
library(ggplot2)
library(maptools)
library(rgeos)
library(sp)
library(mapproj)
library(sf)
library(RStoolbox)
library(ggspatial)
library(cowplot)
library(dplyr)
library(RColorBrewer)
```


# Data

## Raster

```{r}

img = raster("../data/modis/Modis_2003.tif")
```

```{r}
img
```

## Ecozones
```{r}
eco = st_read("../data/ecozones/ne_siberia_ecozones9_ee.shp", "ne_siberia_ecozones9_ee")
```



# Projections 

Russia Equal area projection

```{r}
ea_ru = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs "
```


# Reproject
```{r}
img_ea <- projectRaster(img, crs = ea_ru)

```

```{r}
eco_ea = st_transform(eco, crs=ea_ru)
```

# Crop Raster

DEMcrop1 <- crop(DEM, cropbox1)
# Raster info

```{r}
extent(img_ea)
```


```{r}

hist(img_ea, main="Distribution of values", 
     col= "purple", 
     maxpixels=22000000)
```

```{r}
col <- terrain.colors(1)
image(img_ea, zlim=c(250,375), main="Digital Elevation Model (DEM)", col=col)
```





