---
title: "FLARE-Fire-History-Map"
author: "Anna Talucci"
date: "6/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Overview

Skeleton for developing a map figure for FLARE UAS vegetation paper

This script is reliant on
* `Rproj` and therefore the `wd()`does not have to be set
* Relative path names "../folder-name/file-name.ext"
* This script is reliant on the following folders 
    +"../scripts/" --this houses all scripts written in RMarkdown
    +"../data/shapfiles/" --this houses shape files
    +"../figures/
* Please reference the Git Hub repository called **FLARE-UAV-veg** to see the file structure used here

# Packages

```{r message=FALSE, warning=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(DT)
library(sf)
library(sp)
library(ggmap) # devtools::install_github("dkahle/ggmap")
library(ggrepel)
library(raster)
library(rgdal)
library(rasterVis)
library(RColorBrewer)
library(cowplot)
library(ggspatial)
library(maps)
library(RStoolbox)
library(mapproj)
library(magick)
```

# Projections 

Russia Equal area projection

```{r}
ee_proj = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs "
```

```{r}
laea <- "+proj=laea +lat_0=90 +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs" 
```

# Vector Data

## World 
```{r}
data("wrld_simpl", package = "maptools")                                                                            
wm <- crop(wrld_simpl, extent(-180, 180, 45, 90))                                                                   
plot(wm)  

wm_ee <- spTransform(wm, CRSobj = CRS(laea))
plot(wm_ee)
wm_ee
wm
```

```{r}

wrld_simpl_sf = st_as_sf(wrld_simpl)
```


```{r}
wm_ru <- crop(wrld_simpl, extent(-180, -180, 40, 90))                                                                   
plot(wrld_simpl)
```

## Create a bounding box 

Use metadata from all_fires shapefile to identify `xmin`, `xmax`, `ymin`, and `ymax` to define the bounding box

From raster data below:
Show in New WindowClear OutputExpand/Collapse Output
class      : Extent 
xmin       : 159.9998 
xmax       : 163.0002 
ymin       : 67.24968 
ymax       : 69.25023 


```{r}
(study_area <- data.frame(xmin = 118.0, xmax = 170.0, ymin = 60.0, ymax = 72.0)) #Replace numeric values
```




# World Map

## Worldmap  Arctic view
label = paste0(seq(60, 90, by = 10), "°N")
```{r fig.height=3.5, fig.width=3}
# Defines the x axes required
x_lines <- seq(-120,180, by = 60)

map1 = ggplot() +
  geom_polygon(data = wm, aes(x = long, y = lat, group = group), fill = "wheat", colour = "black", alpha = 0.8) +
  coord_map("ortho", orientation = c(90, 0, 0)) +
  scale_y_continuous(breaks = seq(45, 90, by = 10), labels = NULL) +
  # Removes Axes and labels
  scale_x_continuous(breaks = NULL) +
  xlab("") + 
  ylab("") +
  # Adds labels
  geom_text(aes(x = 0, y = seq(55, 85, by = 10), hjust = -0.2, label = paste0(seq(55, 85, by = 10), "°N"))) +
  geom_text(aes(x = x_lines, y = 44, label = c("120°W", "60°W", "0°", "60°E", "120°E", "180°W"))) +
  # Adds axes
  geom_hline(aes(yintercept = 45), size = 1)  +
  geom_segment(aes(y = 45, yend = 90, x = x_lines, xend = x_lines), linetype = "dashed") +
# Change theme to remove axes and ticks
  theme(panel.background = element_blank(),
      panel.grid.major = element_line(size = 0.25, linetype = 'dashed',
                                      colour = "black"),
      axis.ticks=element_blank())+
  geom_rect(data = study_area, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), alpha = 0, colour = "#000080", size = 1.5, linetype = 1) 


map1
  
```


