---
title: "Flare-FireActivity-StudyArea"
author: "Anna Talucci"
date: "5/10/2021"
output: html_document
---
# Overview

Skeleton for developing a map figure for FLARE UAS vegetation paper

This script is reliant on
* `Rproj` and therefore the `wd()`does not have to be set
* Relative path names "../folder-name/file-name.ext"
* This script is reliant on the following folders 
    +"../scripts/" --this houses all scripts written in RMarkdown
    +"../data/shapfiles/" --this houses shape files
    +"../figures/
* Please reference the Git Hub repository called **FLARE-UAV-veg** to see the file structure used here

# Packages
```{r}
library(rgdal)
library(raster)
library(ggplot2)
library(maptools)
library(rgeos)
library(sp)
library(mapproj)
library(sf)
library(RStoolbox)
library(ggspatial)
library(cowplot)
library(dplyr)
library(RColorBrewer)
```


# Projections 

Russia Equal area projection

```{r}
ea_ru = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs "
```


# Data
https://datacatalog.worldbank.org/dataset/world-bank-official-boundaries

```{r}
wrld = st_read("../data/shapefiles/world/WB_countries_Admin0_10m.shp", "WB_countries_Admin0_10m")
```

```{r}
eco = st_read("../data/ecozones/ne_siberia_ecozones9_ee.shp", "ne_siberia_ecozones9_ee")
```

## Charskiy point
```{r}
cherskiy = st_sf(geometry = st_sfc(st_point(c(161.399713, 68.739907))), crs = ("+proj=longlat +datum=WGS84 +no_defs"))

cherskiy
```

# Arctic Circle 
Arctic Circle shapefile came from [Natural Earth](https://www.naturalearthdata.com/downloads/110m-physical-vectors/110m-geographic-lines/)

```{r}
circle = st_read("../data/ne_110m_geographic_lines/ne_110m_geographic_lines.shp", "ne_110m_geographic_lines") 
```
```{r}
arctic = circle %>% filter(name=="Arctic Circle")
```




# Filter
```{r}
target_cnty = c("Mongolia", "Kazakhstan", "Japan", "People's Republic of China", "Russia", "Uzbekistan")
```

```{r}
target_iso = c("MN", "RU", "CN", "KZ", "KG", "UZ", "JP", "TM")
```

```{r}
target = c("Asia", "Europe")
```
## Apply filter

Filter for all
```{r}
asia  = wrld %>% 
  filter(CONTINENT %in% target) %>%
  dplyr::select( OBJECTID:FORMAL_EN, NAME_EN, ISO_A2, CONTINENT:REGION_WB, Shape_Leng:geometry) 
```



```{r}
asia
```


# Reproject

```{r}
asia_ea = st_transform(asia, crs = ea_ru)
ch_ea = st_transform(cherskiy, crs = ea_ru)
eco_ea = st_transform(eco, crs = ea_ru)
artic_ea = st_transform(arctic, crs = ea_ru)

```

```{r}
plot(asia_ea$geometry)
```

```{r}
asia_ea
```

# Color Palette

```{r}
ecoPalette <- c("#CB453D", "#44CB30", "#2E41C3", "#36A4B4", "#B83491", "#B09C32", "#AE3D5F", "#2DC086", "#3261A1")
```
## Russia Map
xmin: -4334205 ymin: -3922562 xmax: 5433752 ymax: 3493703

+
     xlab("Longitude") + 
   ylab("Latitude") +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), panel.background = element_rect(fill = "aliceblue"))

Background color #C5D8D7

xmin: -13049610 ymin: -6614424 xmax: 6034662 ymax: 11163640

theme(
  panel.background = element_rect(fill = "lightblue",
                                colour = "lightblue",
                                size = 0.5, linetype = "solid"),
```{r}
russia_map3 <- ggplot() +
     geom_sf(data = asia_ea, fill = "#C0C0C0", colour="#A9AB9D") +
      geom_sf(data = eco_ea,  aes(fill=eco_code), colour = NA) +
  geom_sf(data=artic_ea, fill=NA, colour = "#FFFFFF", lwd=1, linetype="dashed") +
  scale_fill_manual(values=ecoPalette) +
coord_sf(xlim = c(-2934205, 4133752), ylim = c(-1122562, 3493703)) +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), panel.background = element_rect(fill = "aliceblue"))


russia_map3
```
