---
title: "Flare-FireActivity-Fronteirs"
author: "Anna Talucci"
date: "5/10/2021"
output: html_document
---
# Overview

Skeleton for developing a map figure for FLARE UAS vegetation paper

This script is reliant on
* `Rproj` and therefore the `wd()`does not have to be set
* Relative path names "../folder-name/file-name.ext"
* This script is reliant on the following folders 
    +"../scripts/" --this houses all scripts written in RMarkdown
    +"../data/shapfiles/" --this houses shape files
    +"../figures/
* Please reference the Git Hub repository called **FLARE-UAV-veg** to see the file structure used here


# Packages
```{r}
library(rgdal)
library(raster)
library(ggplot2)
library(maptools)
library(rgeos)
library(sp)
library(mapproj)
library(sf)
library(RStoolbox)
library(ggspatial)
library(cowplot)
library(dplyr)
library(RColorBrewer)
```


# Projections 

Russia Equal area projection

```{r}
ea_ru = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs "
```


# Data

## World map
https://datacatalog.worldbank.org/dataset/world-bank-official-boundaries

```{r}
wrld = st_read("../data/shapefiles/world/WB_countries_Admin0_10m.shp", "WB_countries_Admin0_10m")
```

## permafrost
```{r}
permafrost = st_read("../data/shapefiles/permafrost/permaice.shp", "permaice")
```

```{r}
head(permafrost)
```

## fires
```{r}
fires = st_read("../data/fires/SiberiaFires2001-2019.shp", "SiberiaFires2001-2019")
```

```{r}
head(fires)
```

## Cities
```{r}
chersky = st_sf(geometry = st_sfc(st_point(c(161.399713, 68.739907))), crs = ("+proj=longlat +datum=WGS84 +no_defs"))

chersky
```

```{r}
yakutsk = st_sf(geometry = st_sfc(st_point(c(129.7422, 62.0397))), crs = ("+proj=longlat +datum=WGS84 +no_defs"))

yakutsk
```

# Arctic Circle 
Arctic Circle shapefile came from [Natural Earth](https://www.naturalearthdata.com/downloads/110m-physical-vectors/110m-geographic-lines/)

```{r}
circle = st_read("../data/ne_110m_geographic_lines/ne_110m_geographic_lines.shp", "ne_110m_geographic_lines") 
```
```{r}
arctic = circle %>% filter(name=="Arctic Circle")
```




# Filter
## Countries
```{r}
target_cnty = c("Mongolia", "Kazakhstan", "Japan", "People's Republic of China", "Russia", "Uzbekistan")
```

```{r}
target_iso = c("MN", "RU", "CN", "KZ", "KG", "UZ", "JP", "TM")
```

```{r}
target = c("Asia", "Europe")
```

Filter for all
```{r}
asia  = wrld %>% 
  filter(CONTINENT %in% target) %>%
  dplyr::select( OBJECTID:FORMAL_EN, NAME_EN, ISO_A2, CONTINENT:REGION_WB, Shape_Leng:geometry) 
```

```{r}
asia
```

## Permafrost
```{r}
perma_con = permafrost %>% 
  filter(EXTENT =="C") 
```

# Reproject

```{r}
asia_ea = st_transform(asia, crs = ea_ru)
ch_ea = st_transform(chersky, crs = ea_ru)
yak_ea = st_transform(yakutsk, crs = ea_ru)
fires_ea = st_transform(fires, crs = ea_ru)
artic_ea = st_transform(arctic, crs = ea_ru)
perma_ea = st_transform(perma_con, crs = ea_ru)
```

```{r}
plot(asia_ea$geometry)
```

```{r}
asia_ea
```

# Color Palette

```{r}
ecoPalette <- c("#CB453D", "#44CB30", "#2E41C3", "#36A4B4", "#B83491", "#B09C32", "#AE3D5F", "#2DC086", "#3261A1")
```
## Russia Map
xmin: -4334205 ymin: -3922562 xmax: 5433752 ymax: 3493703

+
     xlab("Longitude") + 
   ylab("Latitude") +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), panel.background = element_rect(fill = "aliceblue"))

Background color #C5D8D7

xmin: -13049610 ymin: -6614424 xmax: 6034662 ymax: 11163640

theme(
  panel.background = element_rect(fill = "lightblue",
                                colour = "lightblue",
                                size = 0.5, linetype = "solid"),
                                
                                scale_fill_manual(values=ecoPalette) +
```{r fig.height=5, fig.width=6}
sa_legend <- ggplot() +
     geom_sf(data = asia_ea, fill = "#C0C0C0", colour="#A9AB9D") +
    geom_sf(data = perma_ea, fill = "#baf2ef", colour= NA) +
      geom_sf(data = fires_ea,  aes(fill=FireYr), colour = NA) +
  geom_sf(data=artic_ea, fill=NA, colour = "#FFFFFF", lwd=1, linetype="dashed") +
  scale_fill_distiller(palette = "YlOrRd", direction = 1, guide = "colourbar") +
coord_sf(xlim = c(-2934205, 4133752), ylim = c(-1122562, 3493703)) +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), panel.background = element_rect(fill = "aliceblue")) +
  theme(legend.title = element_blank(), legend.position="right", legend.box="vertical", legend.margin=margin()) 


sa_legend
```

```{r}
sa_map <- ggplot() +
     geom_sf(data = asia_ea, fill = "#C0C0C0", colour="#A9AB9D") +
    geom_sf(data = perma_ea, fill = "#dcf3ff", colour= NA) +
      geom_sf(data = fires_ea,  aes(fill=FireYr), colour = NA) +
  geom_sf(data=artic_ea, fill=NA, colour = "#2F4F4F", lwd=1, linetype="dashed") +
    scale_fill_distiller(palette = "OrRd", direction = 1, guide = "colourbar") +
  geom_sf(data=ch_ea, colour="#2F4F4F") +
  geom_sf(data=yak_ea, colour="#2F4F4F") +
  
  coord_sf(xlim = c(-2934205, 4133752), ylim = c(-1122562, 3493703)) +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), panel.background = element_rect(fill = "#C5D8D7")) +
  theme(legend.position="none", axis.text.x=element_blank(),axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
  annotation_scale(location = "bl", width_hint = 0.25, text_size = 12, text_face = "bold", text_family = "sans", text_col = "white") 


sa_map
```

```{r}
legend <- get_legend(
  # create some space to the left of the legend
  sa_legend + theme(legend.box.margin = margin(t = 1, r = 0, b = 1, l = 0,))
)
```

```{r fig.height=5, fig.width=6}

plot1 = cowplot::plot_grid(sa_map, legend, ncol = 1, rel_heights = c(1, .3)) 
plot1
```

```{r fig.height=5, fig.width=6}
plot2 = cowplot::ggdraw(plot1) + 
  draw_label(label="Russia", fontfamily = "sans", fontface = "bold", color = "black", size = 11, hjust = 2, vjust = -1) +

  draw_label(label="Japan", fontfamily = "sans", fontface = "bold", color = "black", size = 11, hjust = -4, vjust = 7) +
  draw_label(label="China", fontfamily = "sans", fontface = "bold", color = "black", size = 11, hjust = -1.8, vjust = 6) +
  draw_label(label="Mongolia", fontfamily = "sans", fontface = "bold", color = "black", size = 11, hjust = 1, vjust = 8.5) +
  draw_label(label="Kazakhstan", fontfamily = "sans", fontface = "bold", color = "black", size = 11, hjust = 2.7, vjust = 5) +
  draw_label(label="Arctic Circle", fontfamily = "sans", fontface = "plain", color = "#2F4F4F", size = 10, hjust = 1, vjust = -6.5) +
  draw_label(label="Yakutsk", fontfamily = "sans", fontface = "plain", color = "#2F4F4F", size = 10, hjust = -1, vjust = -3) +
  draw_label(label="Chersky", fontfamily = "sans", fontface = "plain", color = "#2F4F4F", size = 10, hjust = -1.4, vjust = -13.5) 

plot2
```



```{r}
ggsave("../figures/FLARE_FireActivty_frontiers.png", plot = plot2, width = 6, height = 5, units = c("in"), dpi = 600)
```


# Refernces

Yedoma Citation
Strauss, Jens; Laboor, Sebastian; Fedorov, Alexander N; Fortier, Daniel; Froese, Duane G; Fuchs, Matthias; Grosse, Guido; Günther, Frank; Harden, Jennifer W; Hugelius, Gustaf; Kanevskiy, Mikhail Z; Kholodov, Alexander L; Kunitsky, Victor V; Kraev, Gleb; Lapointe-Elmrabti, Lyna; Lozhkin, Anatoly V; Rivkina, Elizaveta; Robinson, Joel; Schirrmeister, Lutz; Shmelev, Denis; Shur, Yuri; Siegert, Christine; Spektor, Valentin; Ulrich, Mathias; Vartanyan, Sergey L; Veremeeva, Alexandra; Walter Anthony, Katey M; Zimov, Sergey A (2016): Database of Ice-Rich Yedoma Permafrost (IRYP), link to ESRI shapefiles. PANGAEA, https://doi.org/10.1594/PANGAEA.861732,

Retreved from: https://doi.pangaea.de/10.1594/PANGAEA.861732