---
title: "FLARE-GEB-VegMap"
author: "Anna Talucci"
date: "1/21/2022"
output: html_document
---
# Clear workspace

```{r}
rm(list=ls()) 
```

# Overview

Skeleton for developing a map figure for FLARE UAS vegetation paper

This script is reliant on
* `Rproj` and therefore the `wd()`does not have to be set
* Relative path names "../folder-name/file-name.ext"
* This script is reliant on the following folders 
    +"../scripts/" --this houses all scripts written in RMarkdown
    +"../data/shapfiles/" --this houses shape files
    +"../figures/
* Please reference the Git Hub repository called **FLARE-UAV-veg** to see the file structure used here


# Packages
```{r}
library(rgdal)
library(raster)
library(ggplot2)
library(maptools)
library(rgeos)
library(sp)
library(mapproj)
library(sf)
library(RStoolbox)
library(ggspatial)
library(cowplot)
library(dplyr)
library(RColorBrewer)

library(rasterVis)
```


# Projections 

Russia Equal area projection

```{r}
ea_ru = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs "
```

```{r}
wkt_ru = 'PROJCS["Albers Conical Equal Area",GEOGCS["WGS 84",DATUM["WGS_1984",SPHEROID["WGS 84",6378137,298.257223563,AUTHORITY["EPSG","7030"]],TOWGS84[0,0,0,0,0,0,0],AUTHORITY["EPSG","6326"]],PRIMEM["Greenwich",0,AUTHORITY["EPSG","8901"]],UNIT["degree",0.0174532925199433,AUTHORITY["EPSG","9108"]],AUTHORITY["EPSG","4326"]],PROJECTION["Albers_Conic_Equal_Area"],PARAMETER["standard_parallel_1",50],PARAMETER["standard_parallel_2",70],PARAMETER["latitude_of_center",56],PARAMETER["longitude_of_center",100],PARAMETER["false_easting",0],PARAMETER["false_northing",0],UNIT["meters",1]]'
  

```

# Data
## Asia
 "../outputs/Asia_ea/asia_ea.shp"

```{r}
asia = st_read("../data/Asia_ea/asia_ea.shp", "asia_ea")
```

## Fires
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2020.shp", "NESiberiaFires2020")
```
```{r}
st_crs(fires)
```


## Vegetation

```{r eval=FALSE, include=FALSE}
veg<-raster("../data/VegetationRasters/FLARE-Eco-Forest-Percent_clip.tif")
```

```{r}
veg1000<-raster("../data/VegetationRasters/FLARE-Eco-Forest-Percent-clip-scale1000.tif")
```

# Projection

```{r}
veg1000_reprj <- projectRaster(veg1000, crs = crs(ea_ru))

```
```{r}
x2 <- st_crs(fires)
```

```{r}
(x3 <- CRS(SRS_string = x2$wkt))
```
```{r}
w <- wkt(veg1000)
```





# Color Palettes
```{r}
# Assign color to a object for repeat use/ ease of changing
myCol = c('#b2e2e2','#66c2a4','#2ca25f','#006d2c')
myCol2 = c('darkolivegreen1','lightgreen','springgreen4','darkgreen')
```

```{r eval=FALSE, include=FALSE}
png('../figures/vegMap.png', width = 1575, height=945, units = "px")
# plot using breaks.
plot(veg, 
     breaks = c(1, 25, 50, 75, 100), 
     col = myCol2,
     axes=FALSE,
     box=FALSE)
plot(fires,col="transparent",border="red", add = TRUE)
dev.off()
```

```{r}
png('../figures/vegPercentScale1000Map.png', width = 1575, height=945, units = "px")
# plot using breaks.
plot(veg1000, 
     breaks = c(1, 25, 50, 75, 100), 
     col = myCol2,
     axes=FALSE,
     box=FALSE)
plot(fires,col="transparent", border="red", add = TRUE)
dev.off()
```

# Color Palette

```{r eval=FALSE, include=FALSE}
ecoPalette <- c("#CB453D", "#44CB30", "#2E41C3", "#36A4B4", "#B83491", "#B09C32", "#AE3D5F", "#2DC086", "#3261A1")
```

```{r eval=FALSE, include=FALSE}
AlbPalette <- c('#543005','#8c510a','#bf812d','#dfc27d','#f6e8c3','#f5f5f5','#c7eae5','#80cdc1','#35978f','#01665e','#003c30')
```

['#edf8fb','#b2e2e2','#66c2a4','#2ca25f','#006d2c']
```{r}
GreenPalette <- c('#edf8fb','#b2e2e2','#66c2a4','#2ca25f','#006d2c')
```

# Russia Map


limits=c(-.017,.017), breaks=c(-0.015, -0.008,  0.000,  0.008,  0.015)

# Veg Maps
```{r}
ggplot()+
  layer_spatial(veg1000) +
  scale_fill_gradientn(colours=myCol2,  limits=c(1,100), breaks=c(25, 50,  75, 100), na.value = "transparent") +
  geom_sf(data=fires, colour="red")
   
```



```{r fig.height=5, fig.width=6}
ggplot() +
     layer_spatial(veg1000) +
  scale_fill_gradientn(colours=myCol2,limits=c(1,100), breaks=c(25, 50,  75, 100),  na.value = "transparent") +

  
coord_sf(xlim = c(-2934205, 4133752), ylim = c(-1122562, 3493703)) +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), panel.background = element_rect(fill = "aliceblue")) +
  theme(legend.title = element_blank(), legend.position="right", legend.box="vertical", legend.margin=margin()) 



```


  geom_sf(data =  perma_dis_ea, fill = "#DDFFDC", color=NA)+
```{r fig.height=5, fig.width=6}
water_map <- ggplot() +
     geom_sf(data = asia_ea, fill = "#C0C0C0", colour="#A9AB9D") +
  
   layer_spatial(water_crop) +
  scale_fill_gradientn(colours=AlbPalette,limits=c(-.017,.017), breaks=c(-0.015, -0.008,  0.000,  0.008,  0.015),  na.value = "transparent") +
   
  geom_sf(data=artic_ea, fill=NA, colour = "#2F4F4F", lwd=1, linetype="dashed") +

  geom_sf(data=ch_ea, colour="#2F4F4F") +
  geom_sf(data=yak_ea, colour="#2F4F4F") +
  
   coord_sf(xlim = c(-2934205, 4133752), ylim = c(-1122562, 3493703)) +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), panel.background = element_rect(fill = "#C5D8D7")) +
  theme(plot.margin=unit(c(0,0,0,0), "mm"), 
        legend.title = element_blank(), 
        legend.position = c(0.92, 0.25), axis.text.x=element_blank(),axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
  annotation_scale(location = "bl", width_hint = 0.25, text_size = 12, text_face = "bold", text_family = "sans", text_col = "white") 


water_map
```



```{r fig.height=5, fig.width=6}
plot3 = cowplot::ggdraw(water_map) + 
  draw_label(label="Russia", fontfamily = "sans", fontface = "plain", color = "black", size = 11, x=.28, y=.45) +
  draw_label(label="China", fontfamily = "sans", fontface = "plain", color = "black", size = 11, x=.67, y=.23) +
  draw_label(label="Mongolia", fontfamily = "sans", fontface = "plain", color = "black", size = 11,  x=.45, y=.14) +
  draw_label(label="Kazakhstan", fontfamily = "sans", fontface = "plain", color = "black", size = 11,  x=.15, y=.25) +
  draw_label(label="Arctic Circle", fontfamily = "sans", fontface = "plain", angle = -25, color = "black", size = 10,  x=.26, y=.58) +
  draw_label(label="Yakutsk", fontfamily = "sans", fontface = "plain", color = "black", size = 10,  x=.65, y=.5) +
  draw_label(label="Cherskiy", fontfamily = "sans", fontface = "plain", color = "black", size = 10,  x=.65, y=.73)

plot3
```

```{r}
ggsave("../figures/FLARE_Frontiers_water.png", plot = plot3, width = 6, height = 5, units = c("in"), dpi = 600)
```



# Micellaneous
```{r}
legend <- get_legend(
  # create some space to the left of the legend
  sa_legend + theme(legend.box.margin = margin(t = 1, r = 0, b = 1, l = 0,))
)
```

```{r fig.height=5, fig.width=6}

plot1 = cowplot::plot_grid(sa_map, legend, ncol = 1, rel_heights = c(1, .3)) 
plot1
```

```{r fig.height=5, fig.width=6}
plot2 = cowplot::ggdraw(plot1) + 
  draw_label(label="Russia", fontfamily = "sans", fontface = "bold", color = "black", size = 11, hjust = 2, vjust = -1) +

  draw_label(label="Japan", fontfamily = "sans", fontface = "bold", color = "black", size = 11, hjust = -4, vjust = 7) +
  draw_label(label="China", fontfamily = "sans", fontface = "bold", color = "black", size = 11, hjust = -1.8, vjust = 6) +
  draw_label(label="Mongolia", fontfamily = "sans", fontface = "bold", color = "black", size = 11, hjust = 1, vjust = 8.5) +
  draw_label(label="Kazakhstan", fontfamily = "sans", fontface = "bold", color = "black", size = 11, hjust = 2.7, vjust = 5) +
  draw_label(label="Arctic Circle", fontfamily = "sans", fontface = "plain", color = "#2F4F4F", size = 10, hjust = 1, vjust = -6.5) +
  draw_label(label="Yakutsk", fontfamily = "sans", fontface = "plain", color = "#2F4F4F", size = 10, hjust = -1, vjust = -3) +
  draw_label(label="Chersky", fontfamily = "sans", fontface = "plain", color = "#2F4F4F", size = 10, hjust = -1.4, vjust = -13.5) 

plot2
```


```{r}
f <- system.file("external/test.grd", package="raster")
r <- raster(f)
r <- reclassify(r, c(0, 500, 1,
                     500, 2000, 2))
```
```{r}
f
r

```
```{r}
gplot(r) +
    geom_raster(aes(fill = factor(value))) +
    coord_equal()
```

