---
title: "FLARE-Ecozones"
author: "Anna Talucci"
date: "12/6/2021"
output: html_document
---


# Overview

Skeleton for developing a map figure 

This script is reliant on
* `Rproj` and therefore the `wd()`does not have to be set
* Relative path names "../folder-name/file-name.ext"
* This script is reliant on the following folders 
    +"../scripts/" --this houses all scripts written in RMarkdown
    +"../data/shapfiles/" --this houses shape files
    +"../figures/
* Please reference the Git Hub repository called **FLARE-UAV-veg** to see the file structure used here

# Packages
```{r}
library(rgdal)
library(raster)
library(ggplot2)
library(maptools)
library(rgeos)
library(sp)
library(mapproj)
library(sf)
library(RStoolbox)
library(ggspatial)
library(cowplot)
library(dplyr)
library(RColorBrewer)
```


# Projections 

Russia Equal area projection

```{r}
ea_ru = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs "
```


# Data

## World map
https://datacatalog.worldbank.org/dataset/world-bank-official-boundaries

```{r}
wrld = st_read("../data/shapefiles/world/WB_countries_Admin0_10m.shp", "WB_countries_Admin0_10m")
```

## Ecozones
```{r}
eco = st_read("../data/ecozones/ne_siberia_ecozones9_ee.shp", "ne_siberia_ecozones9_ee")
```

```{r}
head(eco)
```

## Cities
```{r}
chersky = st_sf(geometry = st_sfc(st_point(c(161.399713, 68.739907))), crs = ("+proj=longlat +datum=WGS84 +no_defs"))

chersky
```

```{r}
yakutsk = st_sf(geometry = st_sfc(st_point(c(129.7422, 62.0397))), crs = ("+proj=longlat +datum=WGS84 +no_defs"))

yakutsk
```

## Arctic Circle 
Arctic Circle shapefile came from [Natural Earth](https://www.naturalearthdata.com/downloads/110m-physical-vectors/110m-geographic-lines/)

```{r}
circle = st_read("../data/ne_110m_geographic_lines/ne_110m_geographic_lines.shp", "ne_110m_geographic_lines") 
```
```{r}
arctic = circle %>% filter(name=="Arctic Circle")
```

## Permafrost
```{r}
permafrost = st_read("../data/permafrost/permaice.shp", "permaice") 
```

## Yedoma
```{r}
yedoma1 = st_read("../data/IRYP_v1_shapefiles/QG1000k_yedoma_russia.shp", "QG1000k_yedoma_russia") 
yedoma2 = st_read("../data/IRYP_v1_shapefiles/QG2500k_yedoma_russia.shp", "QG2500k_yedoma_russia") 
yedoma3 = st_read("../data/IRYP_v1_shapefiles/SG500k_yedoma_russia.shp", "SG500k_yedoma_russia") 
```

```{r}
head(yedoma1)
head(yedoma2)
head(yedoma3)

```


```{r}
yedoma = dplyr::bind_rows(yedoma1, yedoma2, yedoma3)

```

## Fires

```{r}
fires = st_read("../data/SiberiaFires/SiberiaFires_v2_2001-2020.shp", "SiberiaFires_v2_2001-2020")
```

# Filter

## Filter countries
```{r}
target_cnty = c("Mongolia", "Kazakhstan", "Japan", "People's Republic of China", "Russia", "Uzbekistan")
```

```{r}
target_iso = c("MN", "RU", "CN", "KZ", "KG", "UZ", "JP", "TM")
```

```{r}
target = c("Asia", "Europe")
```

Filter for all
```{r}
asia  = wrld %>% 
  filter(CONTINENT %in% target) %>%
  dplyr::select( OBJECTID:FORMAL_EN, NAME_EN, ISO_A2, CONTINENT:REGION_WB, Shape_Leng:geometry) 
```

```{r}
asia
```

## Filter ecozones
```{r}
eco = eco %>% filter(BIOME!="8")
```


## Filter Permafrost
```{r}
perma_con = permafrost %>% 
  filter(EXTENT =="C") 
```

```{r}
perma_dis = permafrost %>% 
  filter(EXTENT=="D") 
```
## Filter Fire


Convert class to factor
```{r}
fires = fires %>% 
  filter(EcoBiom!="8") %>%
  mutate(BTCodes = ifelse(EcoCode =="EST", "B1",
                  ifelse(EcoCode =="NST", "B2",
                   ifelse(EcoCode =="BT", "T1",
                       ifelse(EcoCode =="CPT", "T2",
                         ifelse(EcoCode =="CKMT", "T3",
                            ifelse(EcoCode =="NSCT", "T4",
                              ifelse(EcoCode =="TCST", "T5", "T6"))))))))

```

```{r}
str(fires)
```

# Reproject

```{r}
asia_ea = st_transform(asia, crs = ea_ru)
ch_ea = st_transform(chersky, crs = ea_ru)
yak_ea = st_transform(yakutsk, crs = ea_ru)
eco_ea = st_transform(eco, crs = ea_ru)
artic_ea = st_transform(arctic, crs = ea_ru)
yedoma_ea = st_transform(yedoma, crs = ea_ru) 
perma_con_ea = st_transform(perma_con, crs = ea_ru) 
perma_dis_ea = st_transform(perma_dis, crs = ea_ru) 
fires_ea = st_transform(fires, crs = ea_ru) 

```

```{r}
plot(asia_ea$geometry)
```

```{r}
asia_ea
```

# Color Palette
```{r}
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```




```{r}
cbbBTCodesPalette <- c("#009E73", "#0072B2", "#000000", "#E69F00", "#56B4E9", "#F0E442", "#CC79A7", "#D55E00")
```

4. EST = B1 = "#009E73",
6. NST = B2 = "#0072B2"
1. BT = T1 = "#000000"
2. CKMT = T2 = "#E69F00"
3. CPT = T3 = "#56B4E9"
5. NSCT = T4 = "#F0E442"
8. TCST = T5 = "#CC79A7"
7. TBBMT = T6 = "#D55E00"

```{r}
eco_ea$eco_code
```

## Russia Map

## Map Eco 8
```{r fig.height=5, fig.width=6}
map_eco8 <- ggplot() +
     geom_sf(data = asia_ea, fill = "#C0C0C0", colour="#A9AB9D") +
      geom_sf(data = eco_ea,  aes(fill=ECO_NAME), colour = NA) +
  geom_sf(data=artic_ea, fill=NA, colour = "#FFFFFF", lwd=1, linetype="dashed") +
  scale_fill_manual(values=cbbPalette, labels = c("BT", "CKMT", "CPT", "EST", "NSCT", "NST", "TCST", "TBBMT")) +
  
  geom_sf(data=ch_ea, colour="#FFFFFF") +
  geom_sf(data=yak_ea, colour="#FFFFFF") +
coord_sf(xlim = c(-2934205, 4133752), ylim = c(-1122562, 3493703)) +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), panel.background = element_rect(fill = "aliceblue")) +
  theme(legend.title = element_blank(), 
        legend.position = c(.5, .05), 
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0)),
         axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y=element_blank(), 
        axis.ticks.y=element_blank(), 
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  guides(fill=guide_legend(ncol=8,byrow=FALSE))


map_eco8
```

## Add Labels
labels=c(expression(paste(6*degree,"E"))

```{r fig.height=5, fig.width=6}
map1 = cowplot::ggdraw(map_eco8) + 
  draw_label(label="Russia", fontfamily = "sans", fontface = "plain", color = "black", size = 11, x=.36, y=.45) +
  draw_label(label="China", fontfamily = "sans", fontface = "plain", color = "black", size = 11, x=.67, y=.2) +
  draw_label(label="Mongolia", fontfamily = "sans", fontface = "plain", color = "black", size = 11,  x=.45, y=.2) +
  draw_label(label="Kazakhstan", fontfamily = "sans", fontface = "plain", color = "black", size = 11,  x=.17, y=.25) +
      draw_label(label="Japan", fontfamily = "sans", fontface = "plain", color = "black", size = 11, x=.85, y=.23) +
  draw_label(label="Arctic Circle", fontfamily = "sans", fontface = "plain", color = "white", size = 10,  x=.45, y=.54) +
  draw_label(label="Yakutsk", fontfamily = "sans", fontface = "plain", color = "white", size = 10,  x=.66, y=.48) +
  draw_label(label="Cherskiy", fontfamily = "sans", fontface = "bold", color = "white", size = 9,  x=.74, y=.715) +
  draw_label(label=(expression(paste(70*degree,"N"))), fontfamily = "sans", fontface = "bold", color = "black",angle= 86, size = 9,  x=.72, y=.84) +
  draw_label(label=(expression(paste(60*degree,"N"))), fontfamily = "sans", fontface = "bold", color = "black",angle= 80, size = 9,  x=.86, y=.84) +
  draw_label(label=(expression(paste(50*degree,"N"))), fontfamily = "sans", fontface = "bold", color = "black",angle= 75, size = 9,  x=.96, y=.65)

map1
```


```{r}
ggsave("../figures/FLARE_Eco8.png", plot = map1, width = 6, height = 5, units = c("in"), dpi = 600)
```



## Map Eco BT


```{r fig.height=5, fig.width=6}
eco_bt = eco_ea %>% filter(eco_code=="BT")

map_eco_bt <- ggplot() +
     geom_sf(data = asia_ea, fill = "#C0C0C0", colour="#A9AB9D") +
      geom_sf(data = eco_bt,  fill="#000000", colour = NA) +
  
  geom_sf(data=artic_ea, fill=NA, colour = "#FFFFFF", lwd=1, linetype="dashed") +
  
  
  
  geom_sf(data=ch_ea, colour="#FFFFFF") +
  geom_sf(data=yak_ea, colour="#FFFFFF") +
coord_sf(xlim = c(-2934205, 4133752), ylim = c(-1122562, 3493703)) +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), panel.background = element_rect(fill = "aliceblue")) +
  theme(legend.title = element_blank(), 
        legend.position = c(.5, .05), 
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0)),
         axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y=element_blank(), 
        axis.ticks.y=element_blank(), 
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  guides(fill=guide_legend(ncol=8,byrow=FALSE))


map_eco_bt

ggsave("../figures/FLARE_Eco_BT.png", plot = map_eco_bt, width = 6, height = 5, units = c("in"), dpi = 600)

```

## Map Eco CKMT


```{r fig.height=5, fig.width=6}
eco_ckmt = eco_ea %>% filter(eco_code=="CKMT")

map_eco_ckmt <- ggplot() +
     geom_sf(data = asia_ea, fill = "#C0C0C0", colour="#A9AB9D") +
      geom_sf(data = eco_ckmt,  fill="#E69F00", colour = NA) +
  
  geom_sf(data=artic_ea, fill=NA, colour = "#FFFFFF", lwd=1, linetype="dashed") +
  
  
  
  geom_sf(data=ch_ea, colour="#FFFFFF") +
  geom_sf(data=yak_ea, colour="#FFFFFF") +
coord_sf(xlim = c(-2934205, 4133752), ylim = c(-1122562, 3493703)) +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), panel.background = element_rect(fill = "aliceblue")) +
  theme(legend.title = element_blank(), 
        legend.position = c(.5, .05), 
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0)),
         axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y=element_blank(), 
        axis.ticks.y=element_blank(), 
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  guides(fill=guide_legend(ncol=8,byrow=FALSE))


map_eco_ckmt

ggsave("../figures/FLARE_Eco_CKMT.png", plot = map_eco_ckmt, width = 6, height = 5, units = c("in"), dpi = 600)

```


## Map Eco CPT


```{r fig.height=5, fig.width=6}
eco_cpt = eco_ea %>% filter(eco_code=="CPT")

map_eco_cpt <- ggplot() +
     geom_sf(data = asia_ea, fill = "#C0C0C0", colour="#A9AB9D") +
      geom_sf(data = eco_cpt,  fill="#56B4E9", colour = NA) +
  
  geom_sf(data=artic_ea, fill=NA, colour = "#FFFFFF", lwd=1, linetype="dashed") +
  
  
  
  geom_sf(data=ch_ea, colour="#FFFFFF") +
  geom_sf(data=yak_ea, colour="#FFFFFF") +
coord_sf(xlim = c(-2934205, 4133752), ylim = c(-1122562, 3493703)) +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), panel.background = element_rect(fill = "aliceblue")) +
  theme(legend.title = element_blank(), 
        legend.position = c(.5, .05), 
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0)),
         axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y=element_blank(), 
        axis.ticks.y=element_blank(), 
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  guides(fill=guide_legend(ncol=8,byrow=FALSE))


map_eco_cpt

ggsave("../figures/FLARE_Eco_CPT.png", plot = map_eco_cpt, width = 6, height = 5, units = c("in"), dpi = 600)

```


## Map Eco EST


```{r fig.height=5, fig.width=6}
eco_est = eco_ea %>% filter(eco_code=="EST")

map_eco_est <- ggplot() +
     geom_sf(data = asia_ea, fill = "#C0C0C0", colour="#A9AB9D") +
      geom_sf(data = eco_est,  fill="#009E73", colour = NA) +
  
  geom_sf(data=artic_ea, fill=NA, colour = "#FFFFFF", lwd=1, linetype="dashed") +
  
  
  
  geom_sf(data=ch_ea, colour="#FFFFFF") +
  geom_sf(data=yak_ea, colour="#FFFFFF") +
coord_sf(xlim = c(-2934205, 4133752), ylim = c(-1122562, 3493703)) +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), panel.background = element_rect(fill = "aliceblue")) +
  theme(legend.title = element_blank(), 
        legend.position = c(.5, .05), 
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0)),
         axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y=element_blank(), 
        axis.ticks.y=element_blank(), 
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  guides(fill=guide_legend(ncol=8,byrow=FALSE))


map_eco_est

ggsave("../figures/FLARE_Eco_EST.png", plot = map_eco_est, width = 6, height = 5, units = c("in"), dpi = 600)

```

## Map Eco NSCT


```{r fig.height=5, fig.width=6}
eco_nsct = eco_ea %>% filter(eco_code=="NSCT")

map_eco_nsct <- ggplot() +
     geom_sf(data = asia_ea, fill = "#C0C0C0", colour="#A9AB9D") +
      geom_sf(data = eco_nsct,  fill="#F0E442", colour = NA) +
  
  geom_sf(data=artic_ea, fill=NA, colour = "#FFFFFF", lwd=1, linetype="dashed") +
  
  
  
  geom_sf(data=ch_ea, colour="#FFFFFF") +
  geom_sf(data=yak_ea, colour="#FFFFFF") +
coord_sf(xlim = c(-2934205, 4133752), ylim = c(-1122562, 3493703)) +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), panel.background = element_rect(fill = "aliceblue")) +
  theme(legend.title = element_blank(), 
        legend.position = c(.5, .05), 
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0)),
         axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y=element_blank(), 
        axis.ticks.y=element_blank(), 
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  guides(fill=guide_legend(ncol=8,byrow=FALSE))


map_eco_nsct

ggsave("../figures/FLARE_Eco_NSCT.png", plot = map_eco_nsct, width = 6, height = 5, units = c("in"), dpi = 600)

```

## Map Eco NST


```{r fig.height=5, fig.width=6}
eco_nst = eco_ea %>% filter(eco_code=="NST")

map_eco_nst <- ggplot() +
     geom_sf(data = asia_ea, fill = "#C0C0C0", colour="#A9AB9D") +
      geom_sf(data = eco_nst,  fill="#0072B2", colour = NA) +
  
  geom_sf(data=artic_ea, fill=NA, colour = "#FFFFFF", lwd=1, linetype="dashed") +
  
  
  
  geom_sf(data=ch_ea, colour="#FFFFFF") +
  geom_sf(data=yak_ea, colour="#FFFFFF") +
coord_sf(xlim = c(-2934205, 4133752), ylim = c(-1122562, 3493703)) +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), panel.background = element_rect(fill = "aliceblue")) +
  theme(legend.title = element_blank(), 
        legend.position = c(.5, .05), 
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0)),
         axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y=element_blank(), 
        axis.ticks.y=element_blank(), 
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  guides(fill=guide_legend(ncol=8,byrow=FALSE))


map_eco_nst

ggsave("../figures/FLARE_Eco_NST.png", plot = map_eco_nst, width = 6, height = 5, units = c("in"), dpi = 600)

```

## Map Eco TCST


```{r fig.height=5, fig.width=6}
eco_tcst = eco_ea %>% filter(eco_code=="TCST")

map_eco_tcst <- ggplot() +
     geom_sf(data = asia_ea, fill = "#C0C0C0", colour="#A9AB9D") +
      geom_sf(data = eco_tcst,  fill="#D55E00", colour = NA) +
  
  geom_sf(data=artic_ea, fill=NA, colour = "#FFFFFF", lwd=1, linetype="dashed") +
  
  
  
  geom_sf(data=ch_ea, colour="#FFFFFF") +
  geom_sf(data=yak_ea, colour="#FFFFFF") +
coord_sf(xlim = c(-2934205, 4133752), ylim = c(-1122562, 3493703)) +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), panel.background = element_rect(fill = "aliceblue")) +
  theme(legend.title = element_blank(), 
        legend.position = c(.5, .05), 
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0)),
         axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y=element_blank(), 
        axis.ticks.y=element_blank(), 
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  guides(fill=guide_legend(ncol=8,byrow=FALSE))


map_eco_tcst

ggsave("../figures/FLARE_Eco_TCST.png", plot = map_eco_tcst, width = 6, height = 5, units = c("in"), dpi = 600)

```


## Map Eco TBBMT


```{r fig.height=5, fig.width=6}
eco_tbbmt = eco_ea %>% filter(eco_code=="TBBMT")

map_eco_tbbmt <- ggplot() +
     geom_sf(data = asia_ea, fill = "#C0C0C0", colour="#A9AB9D") +
      geom_sf(data = eco_tbbmt,  fill="#CC79A7", colour = NA) +
  
  geom_sf(data=artic_ea, fill=NA, colour = "#FFFFFF", lwd=1, linetype="dashed") +
  
  
  
  geom_sf(data=ch_ea, colour="#FFFFFF") +
  geom_sf(data=yak_ea, colour="#FFFFFF") +
coord_sf(xlim = c(-2934205, 4133752), ylim = c(-1122562, 3493703)) +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), panel.background = element_rect(fill = "aliceblue")) +
  theme(legend.title = element_blank(), 
        legend.position = c(.5, .05), 
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0)),
         axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y=element_blank(), 
        axis.ticks.y=element_blank(), 
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  guides(fill=guide_legend(ncol=8,byrow=FALSE))


map_eco_tbbmt

ggsave("../figures/FLARE_Eco_TBBMT.png", plot = map_eco_tbbmt, width = 6, height = 5, units = c("in"), dpi = 600)

```







