---
title: "FLARE-GEB-VegMap"
author: "Anna Talucci"
date: "1/21/2022"
output: html_document
---
# Clear workspace

```{r}
rm(list=ls()) 
```

# Overview

Skeleton for developing a map figure for FLARE UAS vegetation paper

This script is reliant on
* `Rproj` and therefore the `wd()`does not have to be set
* Relative path names "../folder-name/file-name.ext"
* This script is reliant on the following folders 
    +"../scripts/" --this houses all scripts written in RMarkdown
    +"../data/shapfiles/" --this houses shape files
    +"../figures/
* Please reference the Git Hub repository called **FLARE-UAV-veg** to see the file structure used here


# Packages
```{r}
library(rgdal)
library(raster)
library(ggplot2)
library(maptools)
library(rgeos)
library(sp)
library(mapproj)
library(sf)
library(RStoolbox)
library(ggspatial)
library(cowplot)
library(dplyr)
library(RColorBrewer)

library(rasterVis)
```


# Projections 

Russia Equal area projection

```{r}
ea_ru = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs "
```

```{r eval=FALSE, include=FALSE}
wkt_ru = 'PROJCS["Albers Conical Equal Area",GEOGCS["WGS 84",DATUM["WGS_1984",SPHEROID["WGS 84",6378137,298.257223563,AUTHORITY["EPSG","7030"]],TOWGS84[0,0,0,0,0,0,0],AUTHORITY["EPSG","6326"]],PRIMEM["Greenwich",0,AUTHORITY["EPSG","8901"]],UNIT["degree",0.0174532925199433,AUTHORITY["EPSG","9108"]],AUTHORITY["EPSG","4326"]],PROJECTION["Albers_Conic_Equal_Area"],PARAMETER["standard_parallel_1",50],PARAMETER["standard_parallel_2",70],PARAMETER["latitude_of_center",56],PARAMETER["longitude_of_center",100],PARAMETER["false_easting",0],PARAMETER["false_northing",0],UNIT["meters",1]]'
  

```

# Data
## Asia
 "../outputs/Asia_ea/asia_ea.shp"

```{r}
asia = st_read("../data/Asia_ea/asia_ea.shp", "asia_ea")
```

## Fires
```{r}
fires = st_read("../data/NESiberiaFires/NESiberiaFires2020.shp", "NESiberiaFires2020")
```
```{r}
st_crs(fires)
```


## Vegetation

```{r eval=FALSE, include=FALSE}
veg<-raster("../data/VegetationRasters/FLARE-Eco-Forest-Percent_clip.tif")
```

```{r}
veg1000<-raster("../data/VegetationRasters/FLARE-Eco-Forest-Percent-clip-scale1000.tif")
```

```{r}
vegWgs<-raster("../data/VegetationRasters/FLARE-Eco-Forest-Percent-clip-2000-WGS.tif")
```

# Projection

```{r eval=FALSE, include=FALSE}
veg1000_reprj <- projectRaster(veg1000, crs = crs(ea_ru))

```

```{r}
vegwgs_reprj <- projectRaster(vegWgs, crs = crs(ea_ru))

```

```{r}
vegwgs_reprj
```


# Color Palettes
```{r}
# Assign color to a object for repeat use/ ease of changing
myCol = c('#b2e2e2','#66c2a4','#2ca25f','#006d2c')
myCol2 = c('darkolivegreen1','lightgreen','springgreen4','darkgreen')
```

```{r eval=FALSE, include=FALSE}
png('../figures/vegMap.png', width = 1575, height=945, units = "px")
# plot using breaks.
plot(veg, 
     breaks = c(1, 25, 50, 75, 100), 
     col = myCol2,
     axes=FALSE,
     box=FALSE)
plot(fires,col="transparent",border="red", add = TRUE)
dev.off()
```

```{r eval=FALSE, include=FALSE}
png('../figures/vegPercentScale1000Map.png', width = 1575, height=945, units = "px")
# plot using breaks.
plot(st_geometry(asia), col = "#C0C0C0", border = "#A9AB9D")
plot(veg1000, 
     breaks = c(1, 25, 50, 75, 100), 
     col = myCol2,
     axes=FALSE,
     box=FALSE, 
     ext = extent(fires), 
     add=TRUE)
plot(fires,col="transparent", border="red", add = TRUE)
dev.off()
```

```{r eval=FALSE, include=FALSE}
png('../figures/vegPercentWGSMap.png', width = 1575, height=945, units = "px")
# plot using breaks.

plot(vegwgs_reprj, 
     breaks = c(1, 25, 50, 75, 100), 
     col = myCol2,
     axes=FALSE,
     box=FALSE)
plot(fires,col="transparent", border="red", add = TRUE)
dev.off()
```
# Color Palette

```{r eval=FALSE, include=FALSE}
ecoPalette <- c("#CB453D", "#44CB30", "#2E41C3", "#36A4B4", "#B83491", "#B09C32", "#AE3D5F", "#2DC086", "#3261A1")
```

```{r eval=FALSE, include=FALSE}
AlbPalette <- c('#543005','#8c510a','#bf812d','#dfc27d','#f6e8c3','#f5f5f5','#c7eae5','#80cdc1','#35978f','#01665e','#003c30')
```

['#edf8fb','#b2e2e2','#66c2a4','#2ca25f','#006d2c']
```{r}
GreenPalette <- c('#edf8fb','#b2e2e2','#66c2a4','#2ca25f','#006d2c')
```

# Russia Map


limits=c(-.017,.017), breaks=c(-0.015, -0.008,  0.000,  0.008,  0.015)

# Veg Maps
(.15, .83)
```{r fig.height=5, fig.width=6}
p1 = ggplot()+
  geom_sf(data=asia, fill = "#C0C0C0", colour="#A9AB9D") +
  layer_spatial(vegwgs_reprj) +
  scale_fill_gradientn(colours=myCol2,  limits=c(1,100), breaks=c(25, 50,  75, 100), na.value = "transparent", name="Percent tree cover") +
  geom_sf(data=fires, fill=NA, colour = "#c62b27") +
  coord_sf(xlim = c(1024425, 2696481), ylim = c(1044414, 2611519)) +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", size = 0.5), panel.background = element_rect(fill = "#C5D8D7")) +
  
  theme( 
        legend.position = c(.9, .1), 
        legend.box="vertical",
        legend.background = element_rect(fill=alpha('white', 0.5)),
         axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y=element_blank(), 
        axis.ticks.y=element_blank()) 
   
p1
```








```{r}
ggsave("../figures/FLARE_GEB_PercentTrees.png", plot = p1, width = 6, height = 5, units = c("in"), dpi = 600)
```



