---
title: "Flare-FireActivity-StudyArea"
author: "Anna Talucci"
date: "5/10/2021"
output: html_document
---
# Overview

Skeleton for developing a map figure for FLARE UAS vegetation paper

This script is reliant on
* `Rproj` and therefore the `wd()`does not have to be set
* Relative path names "../folder-name/file-name.ext"
* This script is reliant on the following folders 
    +"../scripts/" --this houses all scripts written in RMarkdown
    +"../data/shapfiles/" --this houses shape files
    +"../figures/
* Please reference the Git Hub repository called **FLARE-UAV-veg** to see the file structure used here

# Packages
```{r}
library(rgdal)
library(raster)
library(ggplot2)
library(maptools)
library(rgeos)
library(sp)
library(mapproj)
library(sf)
library(RStoolbox)
library(ggspatial)
library(cowplot)
library(dplyr)
library(RColorBrewer)
```


# Projections 

Russia Equal area projection

```{r}
ea_ru = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs "
```


# Data

## World map
https://datacatalog.worldbank.org/dataset/world-bank-official-boundaries

```{r}
wrld = st_read("../data/shapefiles/world/WB_countries_Admin0_10m.shp", "WB_countries_Admin0_10m")
```

## Ecozones
```{r}
eco = st_read("../data/ecozones/ne_siberia_ecozones9_ee.shp", "ne_siberia_ecozones9_ee")
```

```{r}
head(eco)
```

## Cities
```{r}
chersky = st_sf(geometry = st_sfc(st_point(c(161.399713, 68.739907))), crs = ("+proj=longlat +datum=WGS84 +no_defs"))

chersky
```

```{r}
yakutsk = st_sf(geometry = st_sfc(st_point(c(129.7422, 62.0397))), crs = ("+proj=longlat +datum=WGS84 +no_defs"))

yakutsk
```

## Arctic Circle 
Arctic Circle shapefile came from [Natural Earth](https://www.naturalearthdata.com/downloads/110m-physical-vectors/110m-geographic-lines/)

```{r}
circle = st_read("../data/ne_110m_geographic_lines/ne_110m_geographic_lines.shp", "ne_110m_geographic_lines") 
```
```{r}
arctic = circle %>% filter(name=="Arctic Circle")
```

## Permafrost
```{r}
permafrost = st_read("../data/permafrost/permaice.shp", "permaice") 
```

## Yedoma
```{r}
yedoma1 = st_read("../data/IRYP_v1_shapefiles/QG1000k_yedoma_russia.shp", "QG1000k_yedoma_russia") 
yedoma2 = st_read("../data/IRYP_v1_shapefiles/QG2500k_yedoma_russia.shp", "QG2500k_yedoma_russia") 
yedoma3 = st_read("../data/IRYP_v1_shapefiles/SG500k_yedoma_russia.shp", "SG500k_yedoma_russia") 
```

```{r}
head(yedoma1)
head(yedoma2)
head(yedoma3)

```


```{r}
yedoma = dplyr::bind_rows(yedoma1, yedoma2, yedoma3)

```

## Fires

```{r}
fires = st_read("../data/fires/SiberiaFires2001-2020.shp", "SiberiaFires2001-2020")
```

# Filter

## Filter countries
```{r}
target_cnty = c("Mongolia", "Kazakhstan", "Japan", "People's Republic of China", "Russia", "Uzbekistan")
```

```{r}
target_iso = c("MN", "RU", "CN", "KZ", "KG", "UZ", "JP", "TM")
```

```{r}
target = c("Asia", "Europe")
```

Filter for all
```{r}
asia  = wrld %>% 
  filter(CONTINENT %in% target) %>%
  dplyr::select( OBJECTID:FORMAL_EN, NAME_EN, ISO_A2, CONTINENT:REGION_WB, Shape_Leng:geometry) 
```

```{r}
asia
```

## Filter ecozones
```{r}
eco = eco %>% filter(BIOME!="8")
```


## Filter Permafrost
```{r}
perma_con = permafrost %>% 
  filter(EXTENT =="C") 
```

```{r}
perma_dis = permafrost %>% 
  filter(EXTENT=="D") 
```
## Filter Fire


Convert class to factor
```{r}
fires = fires %>% 
  filter(EcoBiom!="8")
```

```{r}
str(fires)
```

# Reproject

```{r}
asia_ea = st_transform(asia, crs = ea_ru)
ch_ea = st_transform(chersky, crs = ea_ru)
yak_ea = st_transform(yakutsk, crs = ea_ru)
eco_ea = st_transform(eco, crs = ea_ru)
artic_ea = st_transform(arctic, crs = ea_ru)
yedoma_ea = st_transform(yedoma, crs = ea_ru) 
perma_con_ea = st_transform(perma_con, crs = ea_ru) 
perma_dis_ea = st_transform(perma_dis, crs = ea_ru) 
fires_ea = st_transform(fires, crs = ea_ru) 

```

```{r}
plot(asia_ea$geometry)
```

```{r}
asia_ea
```

# Color Palette
```{r}
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

```{r}
ecoPalette <- c("#CB453D", "#44CB30", "#2E41C3", "#36A4B4", "#B83491", "#B09C32", "#AE3D5F", "#2DC086", "#3261A1")
```

```{r}
eco_ea$eco_code
```

## Russia Map
xmin: -4334205 ymin: -3922562 xmax: 5433752 ymax: 3493703

+
     xlab("Longitude") + 
   ylab("Latitude") +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), panel.background = element_rect(fill = "aliceblue"))

Background color #C5D8D7

xmin: -13049610 ymin: -6614424 xmax: 6034662 ymax: 11163640

theme(
  panel.background = element_rect(fill = "lightblue",
                                colour = "lightblue",
                                size = 0.5, linetype = "solid"),
## Legend
```{r eval=FALSE, fig.height=5, fig.width=6, include=FALSE}
sa_legend <- ggplot() +
     geom_sf(data = asia_ea, fill = "#C0C0C0", colour="#A9AB9D") +
      geom_sf(data = eco_ea,  aes(fill=ECO_NAME), colour = NA) +
  geom_sf(data=artic_ea, fill=NA, colour = "#FFFFFF", lwd=1, linetype="dashed") +
  scale_fill_manual(values=cbbPalette, labels = c("BT", "CKMT", "CPT", "EST", "NSCT", "NST", "SSFS",  "TCST", "TBBMT")) +
coord_sf(xlim = c(-2934205, 4133752), ylim = c(-1122562, 3493703)) +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), panel.background = element_rect(fill = "aliceblue")) +
  theme(legend.title = element_blank(), 
        legend.position = c(.5, .1), 
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0)),
         axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y=element_blank(), 
        axis.ticks.y=element_blank(), 
        plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  guides(fill=guide_legend(ncol=9,byrow=FALSE))


sa_legend
```

## Main Map 1
```{r fig.height=5, fig.width=6}
sa_map <- ggplot() +
    geom_sf(data = asia_ea, fill = "#C0C0C0", colour="#A9AB9D") +
    geom_sf(data = eco_ea,  aes(fill=ECO_NAME), colour = NA) +
  scale_fill_manual(values=cbbPalette, labels = c("BT", "CKMT", "CPT", "EST", "NSCT", "NST", "TCST", "TBBMT")) +
    geom_sf(data=artic_ea, fill=NA, colour = "#FFFFFF", lwd=1, linetype="dashed") +
    
  geom_sf(data=ch_ea, colour="#FFFFFF") +
  geom_sf(data=yak_ea, colour="#FFFFFF") +
  coord_sf(xlim = c(-2934205, 4133752), ylim = c(-1122562, 3493703)) +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), 
        panel.background = element_rect(fill = "#C5D8D7")) +
  annotation_scale(location = "bl", width_hint = 0.25, text_size = 12, text_face = "bold", text_family = "sans", text_col = "white") +
  theme(legend.title = element_blank(), 
        legend.position = c(.65, .04), 
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0)),
         axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y=element_blank(), 
        axis.ticks.y=element_blank()) +
  guides(fill=guide_legend(ncol=9,byrow=FALSE))


sa_map
```

## Main Map 2
```{r fig.height=5, fig.width=6}
sa_map2 <- ggplot() +
    geom_sf(data = asia_ea, fill = "#C0C0C0", colour="#A9AB9D") +
  geom_sf(data = perma_con_ea, fill = "#98eff9", colour= NA) +
  geom_sf(data = perma_dis_ea, fill = "#dcf3ff", colour= NA) +
  geom_sf(data = yedoma_ea, fill = "#0EC0A6", colour= NA) +
  geom_sf(data = fires_ea,  aes(fill=FireYr), colour = NA) +

    geom_sf(data=artic_ea, fill=NA, colour = "#FFFFFF", lwd=1, linetype="dashed") +
    scale_fill_distiller(palette = "YlOrRd", direction = 1, guide = "colourbar") +
  coord_sf(xlim = c(-2234205, 3633752), ylim = c(-922562, 3393703)) +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), 
        panel.background = element_rect(fill = "#C5D8D7")) +
  annotation_scale(location = "bl", width_hint = 0.25, text_size = 12, text_face = "bold", text_family = "sans", text_col = "white") +
  theme(legend.title = element_blank(), 
        legend.position = c(.1, .25), 
        legend.box="vertical",
        legend.background = element_rect(fill=alpha('white', 0.0)),
         axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y=element_blank(), 
        axis.ticks.y=element_blank()) 
  


sa_map2
```

### Permafrost Legend
```{r fig.height=5, fig.width=6}
sa_map3 <- ggplot() +
    geom_sf(data = asia_ea, fill = "#C0C0C0", colour="#A9AB9D") +
  geom_sf(data = perma_con_ea, aes(fill = "Continuous"), colour= NA) +
  geom_sf(data = perma_dis_ea, aes(fill = "Discontinuous"), colour= NA) +
  geom_sf(data = yedoma_ea, aes(fill = "Yedoma"), colour= NA) +
  
  scale_fill_manual(values = c("Continuous" = "#98eff9", "Discontinuous" = "#dcf3ff", "Yedoma" = "#0EC0A6"),  labels = c("Continuous", "Discontinuous", "Yedoma"),
                       name = "Legend") +
            

    geom_sf(data=artic_ea, fill=NA, colour = "#FFFFFF", lwd=1, linetype="dashed") +
    
  coord_sf(xlim = c(-2734205, 4133752), ylim = c(-1122562, 3493703)) +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), 
        panel.background = element_rect(fill = "#C5D8D7")) +
  annotation_scale(location = "bl", width_hint = 0.25, text_size = 12, text_face = "bold", text_family = "sans", text_col = "white") +
  theme(legend.title = element_blank(), 
        legend.position = c(.65, .04), 
        legend.key.height = unit(.1, 'in'), 
        legend.key.width = unit(.1, 'in'),
        legend.background = element_rect(fill=alpha('white', 0.0)),
         axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y=element_blank(), 
        axis.ticks.y=element_blank()) +
  guides(fill=guide_legend(ncol=3,byrow=FALSE))

  


sa_map3
```
## Cowplot Legend
```{r}
legend <- get_legend(sa_legend )
```

## Add Labels
labels=c(expression(paste(6*degree,"E"))

```{r fig.height=5, fig.width=6}
map1 = cowplot::ggdraw(sa_map) + 
  draw_label(label="Russia", fontfamily = "sans", fontface = "plain", color = "black", size = 11, x=.36, y=.45) +
  draw_label(label="China", fontfamily = "sans", fontface = "plain", color = "black", size = 11, x=.67, y=.2) +
  draw_label(label="Mongolia", fontfamily = "sans", fontface = "plain", color = "black", size = 11,  x=.45, y=.2) +
  draw_label(label="Kazakhstan", fontfamily = "sans", fontface = "plain", color = "black", size = 11,  x=.17, y=.25) +
      draw_label(label="Japan", fontfamily = "sans", fontface = "plain", color = "black", size = 11, x=.85, y=.23) +
  draw_label(label="Arctic Circle", fontfamily = "sans", fontface = "plain", color = "white", size = 10,  x=.45, y=.54) +
  draw_label(label="Yakutsk", fontfamily = "sans", fontface = "plain", color = "white", size = 10,  x=.66, y=.48) +
  draw_label(label="Cherskiy", fontfamily = "sans", fontface = "bold", color = "white", size = 9,  x=.74, y=.715) +
  draw_label(label=(expression(paste(70*degree,"N"))), fontfamily = "sans", fontface = "bold", color = "black",angle= 86, size = 9,  x=.72, y=.84) +
  draw_label(label=(expression(paste(60*degree,"N"))), fontfamily = "sans", fontface = "bold", color = "black",angle= 80, size = 9,  x=.86, y=.84) +
  draw_label(label=(expression(paste(50*degree,"N"))), fontfamily = "sans", fontface = "bold", color = "black",angle= 75, size = 9,  x=.96, y=.65)

map1
```


```{r}
ggsave("../figures/FLARE_FireActivty_StudyArea.png", plot = map1, width = 6, height = 5, units = c("in"), dpi = 600)
```

## Fire + Permafrost
```{r}
legend2 <- get_legend(sa_map3)
```

```{r fig.height=5, fig.width=6}
map2 = cowplot::ggdraw(sa_map2) + 
  draw_plot(legend2, x=.42, y=.1, width=.5, height=.2) +
   draw_label(label="Permafrost", fontfamily = "sans", fontface = "bold", color = "black", size = 10,  x=.6, y=.14) 

map2
```


```{r}
ggsave("../figures/FLARE_FireActivty_FirePermafrost.png", plot = map2, width = 6, height = 5, units = c("in"), dpi = 600)
```

# References
**Ecozone Shapefile**
Olson, D. M., Dinerstein, E., Wikramanayake, E. D., Burgess, N. D., Powell, G. V. N., Underwood, E. C., D'Amico, J. A., Itoua, I., Strand, H. E., Morrison, J. C., Loucks, C. J., Allnutt, T. F., Ricketts, T. H., Kura, Y., Lamoreux, J. F., Wettengel, W. W., Hedao, P., Kassem, K. R. 2001. Terrestrial ecoregions of the world: a new map of life on Earth. Bioscience 51(11):933-938.

**Yedoma Shapefile**
Strauss, Jens; Laboor, Sebastian; Fedorov, Alexander N; Fortier, Daniel; Froese, Duane G; Fuchs, Matthias; Grosse, Guido; Günther, Frank; Harden, Jennifer W; Hugelius, Gustaf; Kanevskiy, Mikhail Z; Kholodov, Alexander L; Kunitsky, Victor V; Kraev, Gleb; Lapointe-Elmrabti, Lyna; Lozhkin, Anatoly V; Rivkina, Elizaveta; Robinson, Joel; Schirrmeister, Lutz; Shmelev, Denis; Shur, Yuri; Siegert, Christine; Spektor, Valentin; Ulrich, Mathias; Vartanyan, Sergey L; Veremeeva, Alexandra; Walter Anthony, Katey M; Zimov, Sergey A (2016): Database of Ice-Rich Yedoma Permafrost (IRYP), link to ESRI shapefiles. PANGAEA, https://doi.org/10.1594/PANGAEA.861732,

**Permafrost Shapefile**
Brown, J., O. Ferrians, J. A. Heginbottom, and E. Melnikov. 2002. Circum-Arctic Map of Permafrost and Ground-Ice Conditions, Version 2. [Indicate subset used]. Boulder, Colorado USA. NSIDC: National Snow and Ice Data Center. doi: https://doi.org/10.7265/skbg-kf16. [Date Accessed].