---
title: "Map-script"
author: "Anna Talucci"
date: "4/2/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

Skeleton for developing a map figure for FLARE UAS vegetation paper

This script is reliant on
* `Rproj` and therefore the `wd()`does not have to be set
* Relative path names "../folder-name/file-name.ext"
* This script is reliant on the following folders 
    +"../scripts/" --this houses all scripts written in RMarkdown
    +"../data/shapfiles/" --this houses shape files
    +"../figures/
* Please reference the Git Hub repository called **FLARE-UAV-veg** to see the file structure used here

# Packages
```{r}
library(rgdal)                                                                                                      
library(raster)
library(ggplot2)
library(maptools)
library(rgeos)
library(sp)
library(mapproj)
library(sf)
library(RStoolbox)
library(ggspatial)
library(cowplot)
```


# Projections 

Russia Equal area projection

```{r}
ee_proj = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs "
```

```{r}
laea <- "+proj=laea +lat_0=90 +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs" 
```

# Raster Data

## Raster Stack for 3-band RGB Image Satellite Image

```{r}
kr_stack <- stack("../data/satellite/UAV-veg-image-sentinel.tif")
```

```{r}
extent(kr_stack)
```

# Vector Data

## World 
```{r}
data("wrld_simpl")  # from mapproj
```

```{r}
extent(wrld_simpl)
```
```{r}
plot(wrld_simpl)
```
```{r}

wrld_simpl_sf = st_as_sf(wrld_simpl)
```


## Points

### transects


```{r}
plot100_pt = readOGR("../data/shapefiles/field/plot100_pt_sf.shp", "plot100_pt_sf") 
```

```{r}
plot100_pt_sf = st_as_sf(plot100_pt)
plot100_pt_sf
```

### Cherskiy
2141125, 2141260, 2497340, 2497546  (xmin, xmax, ymin, ymax)

x = 161.399713, y = 68.739907,


```{r}
cherskiy = st_point(c(161.399713, 68.739907))
cherskiy
```

```{r}
cherskiy = st_sf(geometry = st_sfc(st_point(c(161.399713, 68.739907))), crs = ("+proj=longlat +datum=WGS84 +no_defs"))

cherskiy
```


## Create a bounding box 

Use metadata from all_fires shapefile to identify `xmin`, `xmax`, `ymin`, and `ymax` to define the bounding box

From raster data below:
Show in New WindowClear OutputExpand/Collapse Output
class      : Extent 
xmin       : 159.9998 
xmax       : 163.0002 
ymin       : 67.24968 
ymax       : 69.25023 

```{r}
(insetrect <- data.frame(xmin = 159.9998, xmax = 163.0002, ymin = 67.24968, ymax = 69.25023)) #Replace numeric values
```

## Russia Map

```{r}
russia_map3 <- ggplot() +
     geom_sf(data = wrld_simpl_sf, fill = "antiquewhite1") +

     coord_sf(xlim = c(70, 170), ylim = c(45, 75)) +
     xlab("Longitude") + 
   ylab("Latitude") +
  geom_rect(data = insetrect, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), alpha = 0, colour = "#000080", size = 1.5, linetype = 1) +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), panel.background = element_rect(fill = "aliceblue"))


russia_map3
```



# Tansect locations
Transect locations on satellite image RGB

```{r}
linecolors = c("#000000", "#000000", "#000000", "#000000")
fillcolors = c("#E69F00", "#CC79A7", "#D55E00", "#F0E442")
```


```{r}
plot_transects5 = ggplot() + 
  ggRGB(kr_stack, r=1, g=2, b=3, ggLayer = TRUE, coord_equal = TRUE) +
  geom_sf(data = cherskiy, size = 4, shape = 24, fill = "grey70") +
     annotate(geom = "text", x = 161.76, y = 68.69, label = "Cherskiy", 
    fontface = "bold", color = "grey70", size = 4) +
  geom_sf(data = plot100_pt_sf, aes(fill = site, color = site),size = 4, shape = 21, alpha= .9) +
  scale_color_manual(values=linecolors) +
  scale_fill_manual(values=fillcolors) +
  scale_y_continuous(breaks = seq(67.5, 69, by = .5), name = "") +
  scale_x_continuous(breaks = seq(161, 162), name = "") +
  
   annotation_north_arrow(location = "bl", which_north = "true", pad_x = unit(0.0, "cm"), pad_y = unit(0.7, "cm"), style = north_arrow_minimal(line_width = 1, line_col = "white", fill = "white", text_size = 0, text_face = NULL, text_family = "sans", text_col = "white")) +
  
  
  annotation_scale(location = "bl", width_hint = 0.25, text_size = 12, text_face = "bold", text_family = "sans", text_col = "white") +
  
  coord_sf(crs = "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0", xlim = c(160.4, 162.4), ylim = c(67.8, 68.8), expand = TRUE) +
  
  theme_classic()+
  
  theme(plot.margin = unit(c(t = 0.2, r = 0.2, b = 0.2, l = 0.2), "cm")) +
    theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "white")) +
  theme(legend.position = "none")
  


plot_transects5

```


# Combining Maps

We combine our study area map with the inset map for a final map figure

```{r}
line1 = data.frame(x1 = 2.86, x2 = 5.2, y1 = 6.6, y2 = 6.25)
line2 = data.frame(x1 = 2.87, x2 = 5.1, y1 = 4.1, y2 = 6.15)
```


```{r fig.height=7, fig.width=6}
fig_maps6 = ggdraw(xlim = c(0, 6), ylim = c(0, 7)) +
    draw_plot(russia_map3, x = 0, y = 3.5, width = 6, height = 3.5) + 
  draw_plot(plot_transects5, x = 0.8, y = 3.75, width = 2.2, height = 3.2,scale =0.9) +

  draw_image("../images/2020-05-22_UAV-Veg-RGB-NDVI-CN.PNG", scale = 0.85, x = 0, y = 0.2, width = 6, height = 3.5) +
  draw_label("Russia", x = 3.5, y = 6, fontfamily = "sans", fontface = "bold", color = "black", size = 12) +
  draw_label("ANS", x = 2.43, y = 4.5, fontfamily = "sans", fontface = "bold", color = "white", size = 10) +
  draw_label("Alnus", x = 1.95, y = 5.1, fontfamily = "sans", fontface = "bold", color = "white", size = 10) +
  draw_label("BP", x = 1.4, y = 5.6, fontfamily = "sans", fontface = "bold", color = "white", size = 10) +
  draw_label("CN", x = 2.15, y = 6.5, fontfamily = "sans", fontface = "bold", color = "white", size = 10) +
  draw_label("161째E", x = 1.67, y = 4.09, fontfamily = "sans", fontface = "plain", color = "black", size = 7) +
   draw_label("162째E", x = 2.47, y = 4.09, fontfamily = "sans", fontface = "plain", color = "black", size = 7) +
  draw_label("68째N", x = 0.95, y = 4.69, fontfamily = "sans", fontface = "plain", color = "black", size = 7, angle = 90) +
  draw_label("68.5째N", x = 0.95, y = 5.74, fontfamily = "sans", fontface = "plain", color = "black", size = 7, angle = 90) +

  draw_label("A", x = 0.3, y = 6.8, fontfamily = "sans", fontface = "bold", color = "black", size = 14) +
   draw_label("B", x = 0.3, y = 3.3, fontfamily = "sans", fontface = "bold", color = "black", size = 14) +
   draw_label("C", x = 3.0, y = 3.3, fontfamily = "sans", fontface = "bold", color = "black", size = 14) +
  geom_segment(data =line1, aes(x = x1, y = y1, xend = x2, yend = y2), linetype = "dotted",  colour = "#000080", size= 1, alpha = .5) +
  geom_segment(data =line2, aes(x = x1, y = y1, xend = x2, yend = y2), linetype = "dotted",  colour = "#000080", size = 1, alpha = .5) 

fig_maps6
```

```{r}
ggsave("../figures/2020-07-12_UAV-Veg-NDVI-RGB.png", plot = fig_maps6, width = 6, height = 7, dpi = 600)
```






